### 2020-06-04 writeup/intro.tex
abstract

\vspace{-0.3in}
\begin{abstract}
\vspace{-0.05in}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine positive vs. negative transfer.
	We formally quantify each component in the setting of high-dimensional linear regression,
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of the multi-task estimator determines the effect of transfer..
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) decreased task similarity;
	(b) increased source sample size; (c) covariate shift under increased source sample size.
	We validate the above results on text classification tasks.
	Inspired by our theory, we show that single-task performance can help understand multi-task performance, and propose an incremental training scheduler for improving the efficiency of multi-task training.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

>>>>

\vspace{-0.3in}
\begin{abstract}
\vspace{-0.05in}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine transfer effect.
	We study the high-dimensional linear regression setting that allows us to define each component precisely,
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size and covariate shift under increased source sample size.
	We validate the three effects on text classification tasks.
	Inspired by our theory, we show two practical connections of interest.
	First, single-task performance can help understand multi-task performance.
	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}
